---
title: "Introduction to StatComp21004"
author: "Tan Zheng"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp21004}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview
In __StatComp21004__ We provide two functions of column generating algorithm to solve large_scale cutting stock problems: __ColGen_CuttingStock__ and __ColGen_CuttingStock2__, where the latter we made minor adjustment on the dual optimization.

## Faster exact optimization algorithm

The problem should be stated that a company only have stocks with $L$ meters, and different customers are in need of stocks of various kinds of length $\{L_{k}\}_{k \in K}$ of different numbers $\{n_{k}\}_{k \in K}$. How to cut those stocks to effeciently use them is a meaningful question to think.

```{r}
library(linprog)
library(Rsymphony)
ColGen_CuttingStock <- function(demand_vec, total_len){
  # Return the number of stocks and cutting plan of each stock.
  # :demand_vec: an n*2 data frame recording customers'
  # demand of different type of stocks.
  # :total_len: int type representing total length of unit stock.
  
  # --------------------------------------------
  # We first calculate a feasible solution.
  n = nrow(demand_vec)
  m = n
  A = diag(ceiling(total_len/demand_vec[,1]-1))
  c = rep(1, m)
  b = demand_vec[,2]
  dir = rep(">=", n)
  res = solveLP(c, b, A, const.dir = dir)
  # --------------------------------------------
  # start the dual part: integer programming.
  dual_c = res$con$dual
  dual_res = Rsymphony_solve_LP(-dual_c, demand_vec[,1], "<=", total_len, types = rep("I", n), max = F)
  reduced_price = 1+dual_res$objval
  # --------------------------------------------
  # When reduced price >= 0, we can terminate the process to get the optimal;
  # or we may add one column to the master problem.
  while(reduced_price < 0){
    new_col = dual_res$solution
    m = m + 1
    A = matrix(cbind(A, new_col), nrow=n)
    c = rep(1, m)
    res = solveLP(c, b, A, const.dir = dir)
    # --------------------------------------------
    # start the dual part: integer programming.
    dual_c = res$con$dual
    dual_res = Rsymphony_solve_LP(-dual_c, demand_vec[,1], "<=", total_len, types = rep("I", n), max = F)
    reduced_price = 1+dual_res$objval
  }
  result = list(value = t(floor(res$solution))%*%t(A)%*%rep(1, n), cutting_plan = A, num_demand = floor(res$solution))
  return(result)
}
```

```{r}
ColGen_CuttingStock2 <- function(demand_vec, total_len){
  # Return the number of stocks and cutting plan of each stock.
  # Different from former function, we add noise on the dual cost trying to get better approximation.
  # :demand_vec: an n*2 data frame recording customers'
  # demand of different type of stocks.
  # :total_len: int type representing total length of unit stock.
  # --------------------------------------------
  # We first calculate a feasible solution.
  sd = 0.01
  n = nrow(demand_vec)
  m = n
  A = diag(ceiling(total_len/demand_vec[,1]-1))
  c = rep(1, m)
  b = demand_vec[,2]
  dir = rep(">=", n)
  res = solveLP(c, b, A, const.dir = dir)
  # --------------------------------------------
  # start the dual part: integer programming.
  dual_c = res$con$dual
  # We tend to find near_optimal sols by adding some noise.
  dual_c = dual_c + rnorm(n, sd=sd)
  dual_res = Rsymphony_solve_LP(-dual_c, demand_vec[,1], "<=", total_len, types = rep("I", n), max = F)
  reduced_price = 1+dual_res$objval
  # --------------------------------------------
  # When reduced price >= 0, we can terminate the process to get the optimal;
  # or we may add one column to the master problem.
  while(reduced_price < 0){
    new_col = dual_res$solution
    m = m + 1
    A = matrix(cbind(A, new_col), nrow=n)
    c = rep(1, m)
    res = solveLP(c, b, A, const.dir = dir)
    # --------------------------------------------
    # start the dual part: integer programming.
    dual_c = res$con$dual
    # We tend to find near_optimal sols by adding some noise.
    dual_c = dual_c + rnorm(n, sd=sd)
    dual_res = Rsymphony_solve_LP(-dual_c, demand_vec[,1], "<=", total_len, types = rep("I", n), max = F)
    reduced_price = 1+dual_res$objval
  }
  result = list(value = t(floor(res$solution))%*%t(A)%*%rep(1, n), cutting_plan = A, num_demand = floor(res$solution))
  return(result)
}

```

## Coding example

```{r}
demand_vec <- matrix(c(3, 6, 7, 25, 20, 18), nrow=3)
total_len = 39
res <- ColGen_CuttingStock(demand_vec, total_len)
res
```

The first result denotes total cost of number, and the __cutting_plan__ item denotes the plan we made on each stock, and the __num_demand__ item shows the corresponding number of stocks.

The use of __ColGen_CuttingStock2__ makes no difference with __ColGen_CuttingStock__, but an enhanced function to help you find more optimal solution.

```{r}
demand_vec <- matrix(c(3, 6, 7, 25, 20, 18), nrow=3)
total_len = 39
res <- ColGen_CuttingStock(demand_vec, total_len)
res
```